---
title: "JKM_1"
author: "Kunal"
date: "12/2/2021"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(RODBC)
library(Hmisc)
library(datasets)
library(shiny)
library(flexdashboard)
library(graphics)
library(shinydashboard)

# load data in 'global' chunk so it can be shared by all users of the dashboard

library(rpivotTable)
library(DT)
library(methods)
library(readr)
library(sodium)
library(shinyjs)
library(shiny)

library(readr)

library(maptools)


df<- mdb.get("UP_124/AC_124.mdb")
Control <- read_excel("UP_124/Control.xlsx")
#S24AC124 <- read_excel("S24AC124.xlsx")
X <- read_excel("colname.xlsx")%>% as.data.frame()

table<- function(df){
  #X<- X[,2]
  modi_df<- matrix(data = NA, nrow = dim(df)[1], ncol = dim(X)[1])
  colnames(modi_df)<- X[,2]
  modi_df<- as.data.frame(modi_df)
  modi_df[1:dim(df)[1],c(1:18, 19)]<- df[1:dim(df)[1], c(1:18, 20)]
  for (i in 1:dim(Control)[1]) {
    modi_df$PartNameEn[modi_df$PartNo== Control$PART_NO[i]]<- Control$PART_NAME_EN[i]
    modi_df$PartName[modi_df$PartNo== Control$PART_NO[i]]<- Control$PART_NAME_V1[i]
  }
  return(modi_df)
}

sub_tbl<- function(dt, Part, section, gender, age_qtl){
  sub<- dt
  R<- quantile(sub$Age)
  if(Part!= "All"){sub <- subset(sub, PartNameEn == Part)}
  if(section!= "All"){sub <- subset(sub, SectionNo == section)}
  if(gender!= "All"){sub <- subset(sub, Sex == gender)}
  if(age_qtl!= "All"){sub <- subset(sub, Age > R[as.numeric(age_qtl)] & Age < R[as.numeric(age_qtl)+1])}
  return(sub)
}
```

 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R datatable can be made interactive by wrapping it in the Shiny `renderDataTable` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
#source("utils.R")
inputPanel(
  selectInput("Part", label = "Part Name:",
              choices = c("All", unique(Control$PART_NAME_EN)), selected = "All"),
  selectInput("section", label = "Section No:",
              choices = c("All", unique(df$SECTION.NO)), selected = "All"),
  selectInput("gender", label = "Gender:",
              choices = c("All", "M", "F"), selected = "All"),
  selectInput("age_qtl", label = "Age Quantile:",
              choices = c("All", "1","2","3","4") , selected = "All"),
  
  actionButton("submit", "Submit")
)
```

Column {.tabset}
-----------------------------------------------------------------------

### Summary
  
```{r, echo= FALSE}
dt<- table(df)

my_data2<- reactive({
  dt_sub<- sub_tbl(dt, input$Part, input$section, input$gender, input$age_qtl)
  return(dt_sub)
})

renderDataTable({
  datatable(summary(my_data2()), extensions = 'Buttons', options = list(
    dom = 'Blfrtip',
    buttons = c('csv', 'excel', 'pdf', 'print'),
    lengthMenu = list(c(10,25,50,-1),c(10,25,50,"All")),
    scrollX = TRUE, scrolly= TRUE
  ))
})
```

### Table

```{r, echo= FALSE}

renderDataTable({
  datatable(my_data2(), extensions = 'Buttons', options = list(
    dom = 'Blfrtip',
    buttons = c('csv', 'excel', 'pdf', 'print'),
    lengthMenu = list(c(10,25,50,-1),c(10,25,50,"All")),
    scrollX = TRUE, scrolly= TRUE
  ))
})
```

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:





